---
title: "Packages"
output: html_document
---

# Packages
Base R is the base library, core where everything starts out.  
There is a ecosystem of packages called tidyverse. When imported it imports a group of packages. They all work with tidy data format.

```{r}
# install.packages('tidyverse')
library(tidyverse)
```

# Clean your data and reshape it
Dplyr with Pipe %>%  
mpg is a built-in dataset from tidyverse (mileage per gallon)  
```{r}
mpg %>% 
  dplyr::filter(manufacturer != 'audi') %>%  # returns all the rows that satisfy condition
  dplyr::arrange(displ, cyl) %>%   # reorder your columns, first orders using displ then cyl
  dplyr::mutate(old = year < 2008) %>% # Preserve previous data, add new column
  # dplyr::transmute(isOld = old == TRUE) %>%  # Drops previous data, add new column
  dplyr::select(-manufacturer) %>%  # Keep or remove columns, Removing manufacturer column and keeping rest
  dplyr::count(model, sort = TRUE) # Creates aggregated stats
```


# Make some graphics
Pipe operator is not in ggplot as of now. So, + is used to kinda pass data
```{r}
# ggplot(data = <DATA>) + 
#   <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) 
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth()
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut))
```

# Examples of EDA ( Explorartory Data Analysis )
```{r}

```

```{r}
smaller <- diamonds %>% 
  filter(carat < 3)
  
ggplot(data = smaller, mapping = aes(x = carat)) +
  geom_histogram(binwidth = 0.3)
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = reorder(class, hwy, FUN = median), y = hwy))
diamonds %>% 
  count(color, cut, sort = T) %>%  
  ggplot(mapping = aes(x = color, y = cut)) +
    geom_tile(mapping = aes(fill = n))
```

# Importing data
```{r}
library(readr)
data <- read_csv("data.csv")
View(data)
```


# Tribble : Different way for creating tables, comes with tidyverse, advance version of data frame
```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
print(preg)
```


# Helper packages
```{r}
# Tribbles are great but they can be a lot to type
# install.packages('datapasta')
library(datapasta)

# In Addins -> DATAPASTA -> Paste as tribble
myData  = tibble::tribble(
  ~carat,        ~cut, ~color, ~clarity, ~depth, ~table, ~price,   ~x,   ~y,   ~z,
    0.23,     "Ideal",    "E",    "SI2",   61.5,    55L,   326L, 3.95, 3.98, 2.43,
    0.21,   "Premium",    "E",    "SI1",   59.8,    61L,   326L, 3.89, 3.84, 2.31,
    0.23,      "Good",    "E",    "VS1",   56.9,    65L,   327L, 4.05, 4.07, 2.31,
    0.29,   "Premium",    "I",    "VS2",   62.4,    58L,   334L,  4.2, 4.23, 2.63,
    0.31,      "Good",    "J",    "SI2",   63.3,    58L,   335L, 4.34, 4.35, 2.75,
    0.24, "Very Good",    "J",   "VVS2",   62.8,    57L,   336L, 3.94, 3.96, 2.48,
    0.24, "Very Good",    "I",   "VVS1",   62.3,    57L,   336L, 3.95, 3.98, 2.47,
    0.26, "Very Good",    "H",    "SI1",   61.9,    55L,   337L, 4.07, 4.11, 2.53,
    0.22,      "Fair",    "E",    "VS2",   65.1,    61L,   337L, 3.87, 3.78, 2.49,
    0.23, "Very Good",    "H",    "VS1",   59.4,    61L,   338L,    4, 4.05, 2.39,
     0.3,      "Good",    "J",    "SI1",     64,    55L,   339L, 4.25, 4.28, 2.73,
    0.23,     "Ideal",    "J",    "VS1",   62.8,    56L,   340L, 3.93,  3.9, 2.46,
    0.22,   "Premium",    "F",    "SI1",   60.4,    61L,   342L, 3.88, 3.84, 2.33,
    0.31,     "Ideal",    "J",    "SI2",   62.2,    54L,   344L, 4.35, 4.37, 2.71,
     0.2,   "Premium",    "E",    "SI2",   60.2,    62L,   345L, 3.79, 3.75, 2.27,
    0.32,   "Premium",    "E",     "I1",   60.9,    58L,   345L, 4.38, 4.42, 2.68,
     0.3,     "Ideal",    "I",    "SI2",     62,    54L,   348L, 4.31, 4.34, 2.68,
     0.3,      "Good",    "J",    "SI1",   63.4,    54L,   351L, 4.23, 4.29,  2.7,
     0.3,      "Good",    "J",    "SI1",   63.8,    56L,   351L, 4.23, 4.26, 2.71,
     0.3, "Very Good",    "J",    "SI1",   62.7,    59L,   351L, 4.21, 4.27, 2.66,
     0.3,      "Good",    "I",    "SI2",   63.3,    56L,   351L, 4.26,  4.3, 2.71,
    0.23, "Very Good",    "E",    "VS2",   63.8,    55L,   352L, 3.85, 3.92, 2.48
  )

print(myData)

```


```{r}
# install.packages('esquisse')
library(esquisse)

# In Addins -> ESQUISSE -> ggplot2 builder -> export and copy code

ggplot(smaller) +
 aes(x = cut, fill = x, colour = color, weight = price) +
 geom_bar() +
 scale_fill_gradient() +
 scale_color_hue() +
 theme_minimal()


# For 3D Data Visualization, study rayshader more
# install.packages('rayshader')
```






