---
title: "Start"
output: html_document
---

## R Objects
- Vectors
- Lists
- Matrices
- Arrays
- Factors
- Data Frames

# Logical TRUE, FALSE
```{r}
v = TRUE
print(class(v))
```


# Numeric
```{r}
x = 23
y = 23.33
print(class(x))
print(class(y))
```


# Integer
```{r}
x = 23L
print(class(x))
```


# Complex
```{r}
x = 23+3i
print(class(x))
```


# Character => Character Vectors are strings
```{r}
x = "HELLO"
print(class(x))
```
```{r}
x = charToRaw("HELLO")
print(class(x))
```


# Create a Vector => c stands for concat or combine
```{r}
# Character Vector
x = c("A", "B", "C")
# Numeric Vector
y = c(1, 2, 3)
print(class(x))
print(class(y))

x = list(c(1, 2, 3), "A", 23.2)
print(class(x))
```



# Matrices
```{r}
x = matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3, byrow = TRUE)
print(x)
```




# Arrays
R does recycling here. Vector of only two values is entered, but dimensions are set to 3, so first value will be recycled and used as 3rd value.
```{r}

x = array(c('green', 'yellow', 'red'), dim = c(4, 3, 1))
print(x)

```


# Factors
Works like an advanced set.
```{r}

x = c('yellow', 'red', 'green', 'green', 'yellow', 'pink')
factorX = factor(x)
print(factorX)
print(nlevels(factorX))
```

# Data Frames
Data Frames are tabular data object. Unlike a matrix, each column can contain different modes of data. It is a list of vectors of equal length. 
There is no null in R. NA should be entered for missing values
```{r}

x = data.frame(
  names  = c('A', 'B', 'C'),
  height = c(12L, 13L, 14L),
  weight = c(44, 55, NA)
)
print(x)
```


# Functions
```{r}
myFunction = function(name) {
  print(paste('Hello', name))
}

myFunction('Dhananjay')
```

#Loops
```{r}
# While Loop
vec = c(1, 2, 3, 4)
i = 1
while(i <= length(vec)) {
  print(vec[i])
  i = i + 1
}
```

```{r}
# For Loop
vec = c(1, 2, 3, 4)
for (counter in 1: length(vec)) {
  print(vec[counter])
}

# Conditional Statement
for (counter in 1: length(vec)) {
  if (vec[counter] != 2) {
    print(vec[counter]) 
  }
}

```










